Homework 2

### 2019-09-12 hw2/MSimonsHW2.tex
Problem 3
Problem 4

>>>>

\item Let $a$ be some element of $\mathbb{Z}/m\mathbb{Z}$.  Assume $a$ is a unit
and let $a^{-1}$ be its inverse.  Also assume $a$ is a zero divisor and let
$ab \equiv 0$ (mod $m$) for some nonzero element $b$ of $\mathbb{Z}/m\mathbb{Z}$
(by definition of zero divisor).
As such,
\[
a^{-1}ab \equiv (a^{-1}a)b \equiv 1b \equiv b (\textrm{mod}\ m)
\]
and
\[
a^{-1}ab \equiv a^{-1}(ab) \equiv a^{-1}(0) \equiv 0 (\textrm{mod}\ m)
\]
Thus, $b \equiv 0$ (mod $m$).  This is a contradiction.  Therefore, $a$ cannot
be a zero divisor and a unit.

\item Let $a$ be some nonzero element of $\mathbb{Z}/m\mathbb{Z}$.  Either $(a,m) = 1$
or $(a,m) > 1$.  First, let $(a,m) = 1$.  If $(a,m) = 1$, then $a$ is a unit
and we are done.  Next, let $(a, m) = c$ for some $c$ such that $c > 1$.
Let $a = {p_0}^{a_0}{p_1}^{a_1} ... {p_k}^{a_k}$ be the prime factorization of
$a$ such that $a_i \geq 0$ for all $i$.
Similarly, let $m = {p_0}^{m_0}{p_1}^{m_1} ... {p_k}^{m_k}$ be the prime factorization of
$m$ such that $m_i \geq 0$ for all $i$.
Since $a$ and $m$ are not relatively prime and $a$ is a nonzero element, there exists
some $d = {p_0}^{max(a_0, m_0)} ... {p_k}^{max(a_k, m_k)}$, which is divisible by $a$
and is a zero element of $\mathbb{Z}/m\mathbb{Z}$.
Let $x = {p_0}^{x_0} ... {p_k}^{x_k}$ such that $x_i \cdot a_i = max(a_i, m_i)$
for all $i$.  Thus, $ax \equiv d \equiv 0$ (mod m).  We know that $x$ is a nonzero
element because $x$ could only be a nonzero element if $x_i = 0$ for all $i$,
implying that $max(a_i, m_i) = 0$ for all $i$ (which would only be true if $a = 1$ and
$p = 1$).  Therefore, if $(a, m) \neq 1$, then $a$ is a zero divisor.
